\documentclass[11pt]{article}

% \usepackage[sort]{natbib}
\usepackage{fancyhdr}

% you may include other packages here (next line)
% \usepackage{enumitem}
\usepackage[ansinew]{inputenc}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{eepic}
\usepackage{amsmath}
% \usepackage{threeparttable}
%\usepackage{amscd}
\usepackage{here}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{array}
\usepackage{calc}
% \usepackage{mwe}
\usepackage{color}
\usepackage{colortbl}
\usepackage{rotating}

\usepackage{caption}
\usepackage{subcaption}

% \usepackage{subfigure}
\usepackage{hyperref}


\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=red,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

%----- you must not change this -----------------

\oddsidemargin -1cm
\evensidemargin -1cm
\topmargin -1.0cm
\textheight 22.0cm
\textwidth 7.3in
\parindent=0pt
%\parskip 1ex
\renewcommand{\baselinestretch}{1.1}
\pagestyle{fancy}
%----------------------------------------------------



% enter your details here----------------------------------

\lhead{\normalsize \textrm{-}}
\chead{}
\rhead{\normalsize Cristian Ocampo}
\lfoot{\normalsize \textrm{}}
\cfoot{}
\rfoot{Meero.}
\setlength{\fboxrule}{4pt}\setlength{\fboxsep}{2ex}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\title{
\vspace{-2cm}
Atelier Git - Meero\hrule
\vspace{-1cm}}   
\date{}

\begin{document}
\maketitle

%----------------your title below -----------------------------
Git: Status $\rightarrow$ add $\rightarrow$ Commit $\rightarrow$ Push

\section{Questions}
\begin{enumerate}
  \item In order to upload my code on certain repository, do I need to have a complete local copy of it in my computer?
  {\color{blue}{Yes, it is necessary to clone the repository locally to make own updates on it.}}
  \item If I created a branch where I added new files, after merging they will appear on master?
  {\color{blue}{Yes, they appear but should be careful. git add files/ git commit -m "Description"/ git checkout master/ git merge BranchName/ git push}}
  \item There is a master for every repository?
  {\color{blue}{No, once a repository is downloaded, folders can be created. To upload the online repository is necessary to add, commit and push.}}
  \item How to kill a branch?
  {\color{blue}{Locally they are killed by: git branch -d Name.}}
\end{enumerate}


\end{document}
              
